\documentclass[a4paper,10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{setspace}

% -----------------------
% Custom section formatting
% -----------------------
\titleformat{\section}{\large\bfseries\uppercase}{\thesection}{1em}{}
\titlespacing{\section}{0pt}{10pt plus 2pt minus 2pt}{5pt}
\setlength{\parskip}{2mm}
\setlength{\parindent}{0pt}

% -----------------------
% CV Information
% -----------------------
\newcommand{\name}{Gursewak Singh}
\newcommand{\email}{Gursewak.singh@gisma-student.com}
\newcommand{\github}{https://github.com/Gursewak266}
\newcommand{\university}{Gisma University of Applied Sciences}
\newcommand{\department}{Department of Computer and Data Sciences}
\newcommand{\location}{Germany}

\begin{document}

% -----------------------
% Header
% -----------------------
\begin{center}
    {\LARGE \textbf{\name}}\\[1mm]
    \department, \university\\
    \location \\
    \faEnvelope\ \email \quad
    \faPhone\ \phone \quad
    \faLinkedin\ \href{https://\linkedin}{\linkedin} \quad
    \faGithub\ \href{https://\github}{\github}
\end{center}

\vspace{3mm}

% -----------------------
% Profile / Summary
% -----------------------
\section*{Profile}
Motivated and highly analytical Computer Science student at \university, specializing in Data Science, Machine Learning, and Web Development. Possess strong programming skills in Python, Java, C++, and web technologies. Experienced in designing, developing, and deploying software projects, with a keen interest in applying data-driven solutions to real-world problems. Proactive, detail-oriented, and eager to contribute to innovative software development projects.

% -----------------------
% Education
% -----------------------
\section*{Education}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Gisma University of Applied Sciences, Germany} \hfill 2024 -- Present\\
    M.Sc. in Computer Science, Department of Computer and Data Sciences\\
    Relevant coursework: Data Structures and Algorithms, Database Systems, Machine Learning, Software Engineering, Web Development
    \begin{itemize}[leftmargin=1.5cm]
    \item Matriculation – 73\%
    \item Intermediate – 78\%
    \item Completed Computer Course
\end{itemize}
\end{itemize}

% -----------------------
% Technical Skills
% -----------------------
\section*{Technical Skills}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Programming Languages:} Python, Java, C++, JavaScript, SQL
    \item \textbf{Web Development:} HTML5, CSS3, JavaScript, Bootstrap, Git, GitHub Pages
    \item \textbf{Data Science \& Machine Learning:} NumPy, Pandas, Matplotlib, Seaborn, Scikit-learn, TensorFlow basics
    \item \textbf{Tools and Software:} LaTeX, VS Code, Jupyter Notebook, Linux, Docker basics
    \item \textbf{Version Control:} Git, GitHub, GitHub Actions
\end{itemize}

% -----------------------
% Projects
% -----------------------
\section*{Projects}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Personal Portfolio Website} -- Developed a professional portfolio using HTML, CSS, JavaScript, and GitHub Pages. Showcases projects, skills, and CV. Integrated responsive design for desktop and mobile.
    \item \textbf{Data Analysis of E-commerce Dataset} -- Collected and analyzed a dataset of 10,000 transactions. Performed data cleaning, visualization, and derived insights on customer behavior using Python and Pandas.
    \item \textbf{Predictive Machine Learning Model} -- Built a regression model to predict housing prices using Scikit-learn. Applied feature engineering, trained multiple models, and evaluated using RMSE and R\textsuperscript{2} score.
    \item \textbf{Inventory Management System} -- Designed a Java-based console application to manage inventory transactions, track stock levels, and generate reports.
    \item \textbf{Simple Web Application} -- Created a responsive CRUD web application using HTML, CSS, JavaScript, and Firebase for storing user data.
\end{itemize}


% -----------------------
% Certifications
% -----------------------
\section*{Certifications}
\begin{itemize}[leftmargin=0.5cm]
    \item Python Programming Certificate -- Coursera
    \item Introduction to Machine Learning -- Udemy
    \item Web Development Bootcamp -- freeCodeCamp
\end{itemize}

% -----------------------
% Achievements
% -----------------------
\section*{Achievements}
\begin{itemize}[leftmargin=0.5cm]
    \item Awarded 'Best Mini Project' in Data Analysis at university coding competition
    \item Ranked in top 10\% of students in Data Structures and Algorithms course
    \item Participated in Hackathon 2024 and developed a real-time web application within 24 hours
\end{itemize}

% -----------------------
% Interests
% -----------------------
\section*{Interests}
Web Development, Machine Learning, Open Source Contributions, Data Analysis, Competitive Programming

% -----------------------
% References
% -----------------------
\section*{References}
Available upon request

\end{document}
